Refinements for open automata

### 2022-07-06 2021-Refinement/paper/refinementarticle.tex
un petit comment Def 7

\begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}. The open automaton \texttt{database}  modelling its behaviour is depicted in Fig. \ref{Fig:SpecOA}. The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}. The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer. When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
\end{example}
\begin{figure}[h]
 \centering
   \includegraphics[width=.9\textwidth]{Figures/database.pdf}
   \caption{Open Automaton. It exposes an unspecified counter in the hole
 to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}}
\end{figure}

@@

\begin{figure}[!tb]
\centering
\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
\caption{The full Traffic Lights system}
\label{fig:tlf}
\end{figure}
\begin{comment}
\subsection{Reachability : check if useful?}
\begin{definition}[Reachability] \label{Def:Reach}
For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
\end{definition}
Reachability takes into account all paths, and can over-approximate the reachable configurations. 
From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary. An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction. We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.

@@

@@

>>>>

\begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}. The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig. \ref{Fig:SpecOA}. The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}. The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer. When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
\end{example}
\begin{figure}[h]
 \centering
   \includegraphics[width=.9\textwidth]{Figures/database.pdf}
   \caption{Open Automaton. It exposes an unspecified counter in the hole
 to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}}
\end{figure}

@@

\begin{comment}
\subsection{Reachability : check if useful?}
\begin{definition}[Reachability] \label{Def:Reach}
For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
\end{definition}

Reachability takes into account all paths, and can over-approximate the reachable configurations. 
From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary. An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction. We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.

@@

This definition leads to a notion of simulation as refinement the same as the one used in LOTOS??? and presented under the name extension refinement.
The extension consists in adding new functionalities by preserving existing ones. Indeed, in case there is no hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
be added, i.e., for traces of the specification (abstract automaton) the implementation (refined automaton) must not add
deadlocks.

@@

\begin{figure}[!tb]
\centering
\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
\caption{The full Traffic Lights system}
\label{fig:tlf}
\end{figure}
